---
title: '1'
output:
  html_document: default
  pdf_document: default
  word_document: default
date: "2023-04-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(magrittr)
library(plyr)
library(dplyr)
library(ggplot2)
```

```{r}
online_carsale = read.csv("C:\\Users\\14154\\Desktop\\DS 311\\group_project\\PushinPythonGroupProject\\sale\\Online_Cars_Sale_Marketplace.csv")
```

1.  

```{r}
online_carsale_clean_1 = online_carsale[online_carsale$Price !="Not Priced",]
class(online_carsale_clean_1$Price) = "intger"
```

2.  

```{r}
online_carsale_clean_1$Used.New = gsub(".*Certified*.", "Certified",online_carsale_clean_1$Used.New)
```

3.  

```{r}
online_carsale_clean_1 = online_carsale[online_carsale$Drivetrain !="–",]
```

4.  

```{r}
popular_mpg = online_carsale_clean_1 %>% group_by(MaxMPG) %>% count() %>% arrange(desc(n))
popular_mpg
```

```{r}
popular_mpg = online_carsale %>% group_by(MaxMPG) %>% count()
g_popular_mpg = ggplot(popular_mpg, aes(MaxMPG, n)) + geom_bar(stat = "identity")
g_popular_mpg_10_50 = g_popular_mpg + scale_x_continuous(limits=c(10, 50))
g_popular_mpg_10_50
```

```{r}
mpg_above_30 = subset(online_carsale_clean_1, MaxMPG >= 30)
mpg_above_30_automatic = mpg_above_30[grep("Automatic", mpg_above_30$Transmission),]
head(mpg_above_30_automatic)
```

```{r}
nrow(mpg_above_30_automatic)
nrow(mpg_above_30)
nrow(mpg_above_30_automatic)/nrow(mpg_above_30) * 100
```

I. What is the most popular car listing on this platform?

```{r}
popular_most = table(online_carsale_clean_1$SellerType)
popular_most
```

```{r}
car_unique_define = online_carsale_clean_1 %>% 
                      group_by('Seller Type' = online_carsale_clean_1$SellerType,
                               'Used/New' = online_carsale_clean_1$Used.New,
                               'Brand' = online_carsale_clean_1$Make, 
                               'Years' = online_carsale_clean_1$Year, 
                               'Model' = online_carsale_clean_1$Model) %>% 
                               count()
head(car_unique_define)
```

• - Define what is popular car listing. Is it number of listings of certain type of car? Rating? Or something else? 

      The of popular car listing is the seller type. People like to purchase car from dealer. 
      
• - How to uniquely define a type of car? By country made, brand, year, etc? 

      The unique define a type of car would be group them by seller type, new/used, make, year,and model.
